### 2010-02-23 trunk/deliverables/D2_4_Mediation/fast_d2_4_2_mediation.tex
version numbers changed
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@591 d8b0c59b-6544-0410-94d9-83a5658a058e

\begin{small}
\begin{tabular}{|l|l|l|p{7.5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{\textbf{Rev. No.}} &
                            \textcolor{white}{\textbf{Date}} &
                            \textcolor{white}{\textbf{Author (Partner)}} &
                            \textcolor{white}{\textbf{Change description}}\\ \hline
0.1 & 09.05.2009 & \authorOne & Initial content \\ \hline
0.4 & 30.11.2009 & \authorOne & Sections 2 and 3 \\ \hline
0.5 & 07.01.2010 & \authorOne & New structure, Section 4 and 5 \\ \hline
0.7 & 03.02.2010 & \authorTwo & Section 3.5, 3.6, updated Section 5  \\ \hline
0.8 & 03.02.2010 & \authorOne & Integration and preliminary finalization  \\ \hline
0.9 & 03.02.2010 & NUIG, UniKassel & Corrections  \\ \hline
1.0 & 03.02.2010 & \authorOne & Integration and finalization  \\ \hline
%0.2 & 19.02.2009 & Oszkar Ambrus (NUIG) & content moved from wiki after internal review \\ \hline
%0.1 & 07.01.2009 & Oszkar Ambrus (NUIG) & final version ready for external review \\ \hline
\end{tabular}
\end{small}

>>>>

\begin{small}
\begin{tabular}{|l|l|l|p{7.5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{\textbf{Rev. No.}} &
                            \textcolor{white}{\textbf{Date}} &
                            \textcolor{white}{\textbf{Author (Partner)}} &
                            \textcolor{white}{\textbf{Change description}}\\ \hline
% 0.1 & 09.05.2009 & \authorOne & Initial content \\ \hline
% 0.4 & 30.11.2009 & \authorOne & Sections 2 and 3 \\ \hline
% 0.5 & 07.01.2010 & \authorOne & New structure, Section 4 and 5 \\ \hline
% 0.7 & 03.02.2010 & \authorTwo & Section 3.5, 3.6, updated Section 5  \\ \hline
% 0.8 & 03.02.2010 & \authorOne & Integration and preliminary finalization  \\ \hline
% 0.9 & 03.02.2010 & NUIG, UniKassel & Corrections  \\ \hline
% 1.0 & 03.02.2010 & \authorOne & Integration and finalization  \\ \hline
%0.2 & 19.02.2009 & Oszkar Ambrus (NUIG) & content moved from wiki after internal review \\ \hline
%0.1 & 07.01.2009 & Oszkar Ambrus (NUIG) & final version ready for external review \\ \hline
1.0 & 27.02.2009 & \authorOne & final version (D2.4.1) ready for external review \\ \hline
2.0 & 27.02.2010 & \authorOne & final version (D2.4.2) ready for external review \\ \hline
\end{tabular}
\end{small}
